### 2025-04-16 thesis/thesis.tex
Set research goals

\section*{List of Abbreviations}
\begin{tabular}{ll}
GPT & Generative Pretrained Transformer \\
SQL & Structured Query Language \\
API & Application Programming Interface \\
% Add other abbreviations as needed
\end{tabular}

@@

This thesis aims to address the aforementioned challanges when it comes to database accessibility.
The following objectives are considered to cover the core research area of this thesis:

\begin{enumerate}
    \item Develop a database extension that can translate natural language queries into semantically
          accurate SQL queries using Large Language Models.
    \item To evaluate the effectiveness and feasibility of different Models aswell as prompt engineering
          techniques in order to improve the performance of the system.
    \item Identify and address issues when it comes to handling amibguous, complex and domain specific user input.
    \item Test the 
\end{enumerate}

>>>>

\section*{List of Abbreviations}
\begin{tabular}{ll}
GPT & Generative Pretrained Transformer \\
SQL & Structured Query Language \\
API & Application Programming Interface \\
LLM & Large Language Model \\
DBMS & Database Management System \\
NL2SQL & Natural Language to SQL \\
\end{tabular}

@@

This thesis aims to address the aforementioned challanges when it comes to database accessibility.
The following objectives are the core research area of this thesis:

\begin{enumerate}
    \item Develop a database extension that can translate natural language queries into semantically
          accurate SQL queries using Large Language Models.
    \item To evaluate the effectiveness and feasibility of different Models aswell as prompt engineering
          techniques in order to improve the performance of the system.
    \item Identify and address issues when it comes to handling amibguous, complex and domain specific user input.
    \item Benchmark the performance of the implementation against common natural language to SQL (NL2SQL) benchmarks.
    \item Idenitfy potential usecases for real world scenarios that could deliver a noticable upsides to users.
    \item Analyze the short commings and limitations of this approach and propose potential solutions to overcome them.
\end{enumerate}
